### 2018-09-21 articleSFDS.tex
changement RMSE et taux de couverture M2'

& $\mathcal{M}_1$ & $\mathcal{M}_2$ & $\mathcal{M}_3$ & $\mathcal{M}_4$ & $\mathcal{M}_2'$&  $\mathcal{M}_4'$ \\
\hline
\hline
coverage rate at 90\% (in \%) & 91 & 32 & 87 & 23 & 54 & 0 \\
\hline
RMSE of the instantaneous power ($W$) & 12.69 & 21.61 & 5.91 & 18.7 & 7.95 & 0 \\
\end{tabular}
\end{table}

@@

The interest of calibration is to assess, in a better way, the error of a quantity of interest. 
For example, Figure \ref{fig:ParamError}, we have introduced the $90\%$ \textit{priori} credibility interval. 
After running calibration for each model, the results illustrate a decrease on this credibility interval (Figure \ref{fig:interestCalibration}).
In the cases of $\mathcal{M}_3$ and $\mathcal{M}_4$, the \textit{posteriori} credibility interval  is mainly represented by the discrepancy .

\begin{figure}[htbp!]
\begin{center}
%   \begin{tabular}{cc}
%   \rotatebox{90}{ \hspace{4em} \small density}
% 	&  \includegraphics[width=.35\textwidth]{figR/model1/densityAr.pdf}\\
%     \end{tabular}
    \begin{tabular}{cccccc}
    & A \textit{priori} & $\mathcal{M}_1$ & $\mathcal{M}_2$ & $\mathcal{M}_3$
    & $\mathcal{M}_4$\\
	\rotatebox{90}{ \hspace{0.5em} \small Power in $W$}
    & \includegraphics[width=.17\textwidth]{figR/credInterPrior.pdf}
    & \includegraphics[width=.17\textwidth]{figR/model1Output.pdf}
    & \includegraphics[width=.17\textwidth]{figR/model2Output.pdf}
    & \includegraphics[width=.17\textwidth]{figR/model3Output.pdf}
    & \includegraphics[width=.17\textwidth]{figR/model4Output.pdf}
    \\
    & \multicolumn{5}{c}{Time in hour}\\
	&&\\
  \end{tabular}   
\caption{The $90\%$ credibility interval a priori is showed on the first panel against the $90\%$ credibility interval a posteriori for each models.}
\label{fig:interestCalibration}
\end{center}
\end{figure}

>>>>

& $\mathcal{M}_1$ & $\mathcal{M}_2$ & $\mathcal{M}_3$ & $\mathcal{M}_4$ & $\mathcal{M}_2'$&  $\mathcal{M}_4'$ \\
\hline
\hline
coverage rate at 90\% (in \%) & 91 & 32 & 87 & 23 & 64 & 0 \\
\hline
RMSE of the instantaneous power ($W$) & 12.69 & 21.61 & 5.91 & 18.7 & 15.42 & 0 \\
\end{tabular}
\end{table}

@@

%The interest of calibration is to assess, in a better way, the error of a quantity of interest. 
%For example, Figure \ref{fig:ParamError}, we have introduced the $90\%$ \textit{priori} credibility interval. 
%After running calibration for each model, the results illustrate a decrease on this credibility interval (Figure \ref{fig:interestCalibration}).
%In the cases of $\mathcal{M}_3$ and $\mathcal{M}_4$, the \textit{posteriori} credibility interval  is mainly represented by the discrepancy .

%\begin{figure}[htbp!]
%\begin{center}
%   \begin{tabular}{cc}
%   \rotatebox{90}{ \hspace{4em} \small density}
% 	&  \includegraphics[width=.35\textwidth]{figR/model1/densityAr.pdf}\\
%     \end{tabular}
%    \begin{tabular}{cccccc}
%    & A \textit{priori} & $\mathcal{M}_1$ & $\mathcal{M}_2$ & $\mathcal{M}_3$
%    & $\mathcal{M}_4$\\
%	\rotatebox{90}{ \hspace{0.5em} \small Power in $W$}
%    & \includegraphics[width=.17\textwidth]{figR/credInterPrior.pdf}
%    & \includegraphics[width=.17\textwidth]{figR/model1Output.pdf}
%    & \includegraphics[width=.17\textwidth]{figR/model2Output.pdf}
%   & \includegraphics[width=.17\textwidth]{figR/model3Output.pdf}
%    & \includegraphics[width=.17\textwidth]{figR/model4Output.pdf}
%    \\
%    & \multicolumn{5}{c}{Time in hour}\\
%	&&\\
%  \end{tabular}   
%\caption{The $90\%$ credibility interval a priori is showed on the first panel against the $90\%$ credibility interval a posteriori for each models.}
%\label{fig:interestCalibration}
%\end{center}
%\end{figure}
